### 2024-04-20 docs/SOSP 2024/related.tex
Fix typos

Some compilers for decision tree ensembles have been proposed in the 
literature \cite{Treelite, Treebeard, Hummingbird}. \TreebeardOLD{} and Treelite
exclusively target CPUs and all their optimizations are designed purely for 
performance on CPUs. 
Treelite\cite{Treelite} is a model compiler that only  
generates \op{if-else} code for each tree in the model. 
\TreebeardOLD{} is the work most closely related to \Treebeard{}. While we 
build on top of \TreebeardOLD{}, \Treebeard{} is a significant enhancement 
over \TreebeardOLD{}. 
Hummingbird\cite{Hummingbird} is a compiler that compiles traditional ML models
to tensor operations, thereby enabling them to be run using tensor-based frameworks like
PyTorch\cite{PyTorch} on CPUs and GPUs. As reported in their paper, Hummingbird's performance
on decision tree models is comparable to that of RAPIDS on GPUs. On CPU, \TreebeardOLD{} 
is faster~\cite{Treebeard}.
% While it can target both CPUs
% and GPUs, its performance has been shown to be lower than that of other frameworks~\cite{Treebeard}.

>>>>

Some compilers for decision tree ensembles have been proposed in the 
literature \cite{Treelite, Treebeard, Hummingbird}. \TreebeardOLD{} and Treelite
exclusively target CPUs and all their optimizations are designed purely for 
performance on CPUs. 
Treelite\cite{Treelite} is a model compiler that only  
generates \op{if-else} code for each tree in the model. 
\TreebeardOLD{} is the work most closely related to \Treebeard{}. While we 
build on top of \TreebeardOLD{}, \Treebeard{} is a significant enhancement 
over \TreebeardOLD{}. 
Hummingbird\cite{Hummingbird} is a compiler that compiles traditional ML models
to tensor operations, thereby enabling them to be run using tensor-based frameworks like
PyTorch\cite{NEURIPS2019_9015} on CPUs and GPUs. As reported in their paper, Hummingbird's performance
on decision tree models is comparable to that of RAPIDS on GPUs. On CPU, \TreebeardOLD{} 
is faster~\cite{Treebeard}.
% While it can target both CPUs
% and GPUs, its performance has been shown to be lower than that of other frameworks~\cite{Treebeard}.

### 2024-04-20 docs/SOSP 2024/results.tex
Change section title. Move figures in results
Fix typos

@@

\begin{figure*}[htb]
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
      \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size}      
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024}
    \end{subfigure}
    \begin{subfigure}[t]{.32\linewidth}
      \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
      \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192}
    \end{subfigure}
    % \hfill
    \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
    benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs shows the kernel time speedup of \Treebeard{} per benchmark. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    \caption{Batch size 512}
  \end{subfigure}
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    \caption{Batch size 4096}
  \end{subfigure}
  \caption{\label{fig:randomModels4060}Kernel time speedup of \Treebeard{} over RAPIDS for random models.
  }
\end{figure}

@@

\subsubsection*{Schedule Sensitivity Across GPUs}
We designed additional experiments to evaluate whether the best schedule (as picked by the heuristic) from one GPU can be used on another.
Figure \ref{Fig:AutotuningSpeedupvs4060Sched} reports the Geomean performance improvements of using the best schedule on T400 and MI210 compared to using the best schedule found on the RTX 4060 (for a given batch size).
As can be seen the T400 specific schedule is 1.05$\times$ to 1.2$\times$ better 
with the maximum difference being $2\times$ (\op{epsilon} at batch size 512).
There is a much larger variation in performance on MI120. For example, 
the geomean speedup over all benchmarks is 1.5$\times$ at batch size 16k (maxiumum 2$\times$ for the \op{letters} benchmark).
In conclusion, schedules found on one GPU do not carry over to other GPUs and often result in sub-optimal performance.
It is necessary tune schedules on each target to achieve the best performance.

\begin{figure*}[htb]
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
  \caption{Speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA T400.}
  \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Slowdown of heuristic schedule vs best schedule on NVIDIA RTX 4060 and 
  heuristic schedule exploration time normalized w.r.t full schedule exploration time.}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of using a hardware specific schedule on NVIDIA T400 and AMD MI210 over the best schedule from a different hardware (NVIDIA RTX 4060).}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{minipage}
\end{figure*}

@@

\subsection{Additional Observations}
%Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are infact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.

>>>>

\begin{figure*}[htb]
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
    \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size.}      
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024.}
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192.}
  \end{subfigure}
  % \hfill
  \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs shows the kernel time speedup of \Treebeard{} per benchmark. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b512_depth8.png}
    \caption{Batch size 512.}
  \end{subfigure}
  \begin{subfigure}[t]{.475\linewidth}
    \includegraphics[width=\linewidth]{figures/RandomModels/kernel_speedup_b4096_depth6.png}
    \caption{Batch size 4096.}
  \end{subfigure}
  \caption{\label{fig:randomModels4060}Kernel time speedup of \Treebeard{} over RAPIDS for random models.
  }
\end{figure}

\begin{figure*}[h]
  \begin{minipage}[t]{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
    \caption{Speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
    benchmarks) across batch sizes on NVIDIA T400.}
    \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[t]{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
    \caption{Slowdown of heuristic schedule vs best schedule on NVIDIA RTX 4060 and 
    heuristic schedule exploration time normalized w.r.t full schedule exploration time.}
    \label{Fig:HeuristicVsFullExplore_Speedup}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[t]{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
    \caption{Geomean speedup of using a hardware specific schedule on NVIDIA T400 and AMD MI210 over the best schedule from a different hardware (NVIDIA RTX 4060).}
    \label{Fig:AutotuningSpeedupvs4060Sched}
  \end{minipage}
  \end{figure*}

@@

\subsubsection*{Schedule Sensitivity Across GPUs}
We designed additional experiments to evaluate whether the best schedule (as picked by the heuristic) from one GPU can be used on another.
Figure \ref{Fig:AutotuningSpeedupvs4060Sched} reports the Geomean performance improvements of using the best schedule on T400 and MI210 compared to using the best schedule found on the RTX 4060 (for a given batch size).
As can be seen the T400 specific schedule is 1.05$\times$ to 1.2$\times$ better 
with the maximum difference being $2\times$ (\op{epsilon} at batch size 512).
There is a much larger variation in performance on MI120. For example, 
the geomean speedup over all benchmarks is 1.5$\times$ at batch size 16k (maximum 2$\times$ for the \op{letters} benchmark).
In conclusion, schedules found on one GPU do not carry over to other GPUs and often result in sub-optimal performance.
It is necessary tune schedules on each target to achieve the best performance.

@@

\subsection{Additional Observations}
%Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are in fact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.
